Through the eyes of the teacher

### 2021-11-28 01_studies/01_Laborstudie ProVisioNET/R script/demographic data/demographic data script.Rmd
r script demo data
SJT + SRI Plots

# prepare data (selected from questionnaire data)
demo.data <- read_excel ("./data/data_empschul_labor_lehrperson_2021-11-24.xlsx")

@@

>>>>

# prepare data (selected from questionnaire data)
demo.data <- read_excel ("./data/data_empschul_labor_lehrperson.xlsx")

@@

# changing gender female 2 = 0 
demo.data$Gender = ifelse(demo.data$Gender == 2, "0","1")

# changing character into numeric
demo.data$Gender <- as.numeric(demo.data$Gender)
